Reproducibility and Open Science in Economics

### 2025-03-06 article.tex
Updates from Overleaf

How onerous are access restrictions in general? In my work as Data Editor, it matters less than it would seem at first blush. The AEA asks that authors, when submitting, provide some information on how restrictive the data used in the article are, and whether the authors are able to provide the data editor with a not-for-publication copy, for the purpose of verification.\footnote{\href{https://www.aeaweb.org/journals/forms/data-code-availability}{Data and Code Availability Form}} Table~\ref{tab:categories} lists the four levels of restrictions, with some guidance on how to classify specific data. Authors can list multiple categories, and we review these, possibly adjusting them before we record them in our internal database.

@@

Table~\ref{tab:restrictions}
\input{outputs/table_access_provision}

>>>>

How onerous are access restrictions in general? In my work as Data Editor, it matters less than it would seem at first blush. The AEA asks that authors, when submitting, provide some information on how restrictive the data used in the article are, and whether the authors are able to provide the data editor with a not-for-publication copy, for the purpose of verification.\footnote{\href{https://www.aeaweb.org/journals/forms/data-code-availability}{Data and Code Availability Form}} Table~\ref{tab:categories} lists the four levels of restrictions, with some guidance on how to classify specific data. Access via research data centers, described earlier, generally fit within the `moderately difficult to obtain` category. Many private-sector datasets, relying on personal interactions with individuals within the company, fall into the `very difficult to obtain', because others may never be able to obtain them. Authors can list multiple categories, and we review these, possibly adjusting them before we record them in our internal database.

@@

Table~\ref{tab:access_provision} lists the distribution of the four levels of restrictions, in addition to the no-restriction category, interacted with whether the authors offered to share the files with the data editor. 
\input{outputs/table_access_provision}
